---
title: "baap"
output: html_document

---

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![R-CMD-check](https://github.com/masiraji/baap/workflows/R-CMD-check/badge.svg)](https://github.com/masiraji/baap/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/baap)](https://CRAN.R-project.org/package=baap)
<!-- badges: end -->



This is a companion r package for the Book " Basic and Advanced Psychometrics in R" [work in Progress]

This package includes data-frames and some interesting commands. Over the years I have come across many useful chunk of codes in Stak overflow and Github. I have included some of those codes in this package. Whenever possible I have tried to mention the original source of the code in the description.

## Installation

You can install the development version of baap from [GitHub](https://github.com) with:

```{r, eval=F, echo=T}
# install.packages("devtools")

devtools::install_github("masiraji/baap")

```


## Example

### Creating A Summary Table of Factor Analysis
Commonly it is very difficult to create a publication friendly table that summaries all necessary information of a factor analysis. This example will help you in that pursuit.
```{r FA,  echo =T, warning=F, message=F}
#load the required libraries
library(baap)
library(tidyverse)
library(psych)
library(papaja)

#Load the data from baap package
data <- baap::Rotter[, 11:31]
# Create a correlational matrix to compute factor analysis
correlations <- psych::polychoric(data, correct = 0)

fa.5F.1 <- psych::fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
residuals = TRUE, SMC = TRUE, n.obs =428)


table <- baap::fac.tab(fa.5F.1, .3, complexity = F)

papaja::apa_table(table, caption= "A Beautiful Table describing the Fator analysis Output ")



```


### Creating A Summary Table of Fit indices in Confitmatory Factor Analyis

When reporting the results of confirmatory factor analysis, modern psychometrics suggest to fit several possible structural model of the latent construct and report the fit indices for them. [**lavan**](https://github.com/yrosseel/lavaan)  package does fantastic job doing the confirmatory factor analysis. Here we will see how to create publication friendly summary of fit indices from several fitteted model
```{r CFA, echo =T, warning=F, message=F}
# Load required packages
library(baap)
library(tidyverse)
library(lavaan)
library(papaja)

# load the data
data <- baap::FFMQ.CFA

# First CFA model

FF.model.Original <- "Observe =~ item1 + item6 + item11 + item15 +item20 + item26 + item31 + item 36
Describe =~ item2 + item7 + Ritem12 + Ritem16 + Ritem22 + item27 +
item32 + item37
Awareness =~ Ritem5 + Ritem8 + Ritem13 + Ritem18 + Ritem23 + Ritem28 + Ritem34 + Ritem38
Nonjudge =~ Ritem3 + Ritem10 + Ritem14 + Ritem17 + Ritem25 + Ritem30+ Ritem35 + Ritem39
Nonreact =~ item4 + item9 + item19 + item21 + item24 + item29 + item33 "

fit.original <- lavaan::cfa(FF.model.Original, data = data, estimator = "MLR", mimic = "Mplus")

# Second CFA Model
FF.model.Cor <-  "Observe =~ item1 + item6 + item11 + item15 +item20 + item26 + item31 + item 36
Describe =~ item2 + item7   + item27 + item32 + item37
Awareness =~ Ritem5 + Ritem8 + Ritem13 + Ritem18 + Ritem23 +Ritem28 + Ritem34
Nonjudge =~  Ritem10 + Ritem14 + Ritem25 + Ritem30+ Ritem35
Nonreact =~ item4 + item9 + item19 + item21 + item24 + item29 + item33
Ritem28 ~~ Ritem34
Ritem23 ~~ Ritem34"
fit.Cor <- lavaan::cfa(FF.model.Cor, data = data, estimator = "MLR", mimic = "Mplus")

# Third CFA Model
FF.short <- "Observe =~ item36 + item26 +item20 + item11
Describe =~ item2 + item7 + item27 +  item32
Awareness =~  Ritem8 + Ritem13 + Ritem23 + Ritem28
Nonjudge =~ Ritem10  + Ritem25 + Ritem30 + Ritem35
Nonreact =~ item9 + item19 + item21 + item24"

fit.short <- lavaan::cfa(FF.short, data = data, estimator = "MLR", mimic = "Mplus")

# Creating Summary table of fit indices from three fitted model (lavaan class objects)

table <- cfa.tab.multi(fit.original, fit.Cor, fit.short, robust = TRUE)

papaja::apa_table(table, caption= "A Beautiful Table describing the Fit Indices of Three Fitted Model ")

```

### Creating Summary Table for Item Analysis
In psychometrics conducting item analysis is very common. [**psych**](https://cran.r-project.org/web/packages/psych/index.html) packages have provided enough tools to smoothly run the item analysis. Here we will create publication friendly summary table of item analysis with all necessary information using function **des.tab()**

```{r ItemAnalysis,echo =T, warning=F, message=F }
#Load required packages
library(baap)
library(tidyverse)
library(psych)

#load Ddta
data <- baap::Rotter[, 11:31]
table <- des.tab(data)
papaja::apa_table(table, caption= "A Beautiful Table Summarizing the Output of Item Analysis ")

```

